%(bulleted; list of tasks, activities and deliverable documents that shall be developed in order to achieve the goal of the project or study).


\section{Scope}
The main objective of this study is to develop different simulation codes to find numerical computational solutions to solve different cases in which the equations of mass, momentum and energy are applied.
\\
The first step will be to solve some basic cases in order to learn the fundamentals of the mathematical formulation and the computational and programming techniques that are going to be needed to develop the whole study. With the help of these cases, some simulation codes are going to be developed.
\newline
Finally, a second part of this study will be to apply the knowledge acquired to a practical case, that may be an engineering system or any other physical system.
\newline
\newline
In order to accomplish the objectives mentioned above, these are the following tasks to be developed:
\begin{itemize}
	\item Previous research of the state of the art.
	\item Theoretical approach of the fluid dynamics behind all the cases and study of the mathematical formulation that should be applied.
	\item Development of the necessary numerical simulation tools. All the codes will need to be validated to ensure they are correct.
	\item Application of the developed simulation codes to an specific system and possible optimization of this system through them.
	\item Analysis of the obtained results.
	\item Conclusions
\end{itemize}
